Simulation connectance richness

### 2023-05-17 report/cs_analysis.Rmd
Update report

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE,
  fig.path="figures/"
)
```

@@

library(rpart)
library(rpart.plot)
library(caret)
library(ipred)

@@

- Response diversity is key in driving stability in ecological communities
- Response diversity control asynchrony with richness
- Mainly done in plants
- Food-webs structure can also modulate synchrony by predator-prey relationships
- Interaction strength, connectance, richness and enrichment can also drive more

@@

@@

# What is the effects of species richness on stability facing multiple stressors in competitive and food-webs communities?

@@

- Important bits:
  - Niche model (Connectance highly constrained by richness)
  - Type III functional response
  - No predator interference
  - Standardize carrying capacity? (Remove the effect of species richness on
    total biomass, i.e. remove the effect of niche complementarity on biomass
    produced by primary producers)

@@

- S: 5 to 60
- C: .02 to .3
- K: 1 and 20
- $\rho$: 0 to 1
- Z: 10 to 1000

@@

```{r}
simZ %>%
  filter(rho == 0) %>%
  pivot_longer(
    c(stab_com, stab_pop, sync, total_biomass),
    names_to = "metric",
    values_to = "stab") %>%
  ggplot(aes(x = richness, y = stab, color = factor(env_stoch))) +
  geom_point() +
  facet_grid(rows = vars(metric), cols = vars(productivity), scales = "free_y") +
  labs(
    color = "Evironmental stochasticity",
    x = "Species richness",
    y = "Stability component"
  )
```

@@

```{r}
cor_enrich <- cor(simZ %>%
    filter(productivity == "enrichment") %>%
    select(c(S, richness, ct, Z, ct_alive, total_biomass, avg_max_int_alive,
        w_avg_tlvl_alive, max_tlvl_alive, rho, env_stoch, stab_com, avg_cv_sp,
        sync)),
    method = "spearman")
cor_basic <- cor(simZ %>%
    filter(productivity == "basic") %>%
    select(c(S, richness, ct, Z, ct_alive, total_biomass, avg_max_int_alive,
        w_avg_tlvl_alive, max_tlvl_alive, rho, env_stoch, stab_com, avg_cv_sp,
        sync)),
    method = "spearman")
p_cor_basic <- ggcorrplot(cor_basic, type = "lower",
   lab = TRUE)
p_cor_enrich <- ggcorrplot(cor_enrich, type = "lower",
   lab = TRUE)
p_cor <- plot_grid(
  p_cor_basic,
  p_cor_enrich,
  ncol = 2
)
ggsave(here("report", "figures", "p_cor.pdf"),
  plot = p_cor,
  device = NULL,
  path = NULL,
  scale = 3.0,
  units = "mm",
  width = 140,
  height = 140 * .5,
  dpi = 300,
  limitsize = TRUE,
  bg = NULL
)
```

- Main results:
  - Stability increases with richness but not connectance (no overall effect)
  - Richness increases stability by increasing maximum and average trophic
    level, but also by decreasing interaction strength and increasing asymetry
    in trophic interaction, and finally by increasing total biomass (I need to control for that).
  - Synchrony decreases with species richness, max and average trophic level but increases with
    average interaction strength and symetry of interaction distributions.
  - Population varibility decreases with species richness, average and maximum
    trophic level, asymetry of interaction strength but it is increased by
    average interaction strength
  - Same effects of food-web structure on both Synchrony and Population variability
    - Surpringly, as in Danet et al. (2021), connectance has little effect on
      temporal stability and its components!

```{r}
sim_rich_prod <- simZ %>%
  filter(
    Z == 100,
    env_stoch == .5,
    rho %in% c(0, 1)
  )
```

```{r}
p_sim_rich_prod <- sim_rich_prod %>%
  mutate(stab_pop = 1/ avg_cv_sp) %>%
  pivot_longer(
    c(stab_com, stab_pop, sync),
    names_to = "metric",
    values_to = "stab") %>%
  mutate(
    metric = var_replacement()[metric],
    rho = rho_replacement()[as.character(rho)]
  ) %>%
  ggplot(aes(x = richness, y = stab, color = factor(productivity))) +
  geom_point(alpha = .1, shape = 20) +
  geom_smooth() +
  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
  labs(
    color = "Productivity",
    x = "Species richness",
    y = "Stability component"
  ) +
  scale_x_continuous(
    sec.axis = sec_axis(~ . ,
      name = "Response diversity",
      breaks = NULL,
      labels = NULL)
  )
ggsave(
  filename = here::here("fig", "stability_rich.pdf"),
  p_sim_rich_prod,
  scale = 1.8,
  width = 88,
  height = 88 * .6,
  units = "mm"
)
```

```{r}
p_sim_rich_prod <- sim_rich_prod %>%
  filter(ct_alive != 0) %>%
  mutate(stab_pop = 1/ avg_cv_sp) %>%
  pivot_longer(
    c(stab_com, stab_pop, sync),
    names_to = "metric",
    values_to = "stab") %>%
  mutate(
    metric = var_replacement()[metric],
    rho = rho_replacement()[as.character(rho)]
  ) %>%
  ggplot(aes(x = richness, y = stab, color = factor(productivity))) +
  geom_point(alpha = .1, shape = 20) +
  geom_smooth() +
  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
  labs(
    color = "Productivity",
    x = "Species richness",
    y = "Stability component"
  ) +
  scale_x_continuous(
    sec.axis = sec_axis(~ . ,
      name = "Response diversity",
      breaks = NULL,
      labels = NULL)
  )
ggsave(
  filename = here::here("fig", "stability_rich_fw_only.pdf"),
  p_sim_rich_prod,
  scale = 1.8,
  width = 88,
  height = 88 * .6,
  units = "mm"
)
```

```{r}
p_sim_rich_prod_p_only <- sim_rich_prod %>%
  filter(ct_alive == 0) %>%
  mutate(stab_pop = 1/ avg_cv_sp) %>%
  pivot_longer(
    c(stab_com, stab_pop, sync),
    names_to = "metric",
    values_to = "stab") %>%
  mutate(
    metric = var_replacement()[metric],
    rho = rho_replacement()[as.character(rho)]
  ) %>%
  ggplot(aes(x = richness, y = stab, color = factor(productivity))) +
  geom_point(alpha = .1, shape = 20) +
  geom_smooth() +
  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
  labs(
    color = "Productivity",
    x = "Species richness",
    y = "Stability component"
  ) +
  scale_x_continuous(
    sec.axis = sec_axis(~ .,
      name = "Response diversity",
      breaks = NULL,
      labels = NULL)
  )
ggsave(
  filename = here::here("fig", "stability_rich_p_only.pdf"),
  p_sim_rich_prod_p_only,
  scale = 1.8,
  width = 88,
  height = 88 * .6,
  units = "mm"
)
```

# Covariation

@@

```{r}
sim_sem <- simZ %>%
  filter(rho == 0) %>%
  mutate(across(c(async, sync, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}")) %>%
  mutate(
    log1_avg_max_int_alive = log(avg_max_int_alive + 1),
    productivity_f = factor(productivity)

    ) %>%
  as.data.frame() %>%
  select(c(
      ct_alive, log_richness, max_tlvl_alive, Z,
      gini_max_int, avg_max_int_alive, log1_avg_max_int_alive, env_stoch,
      log_stab_com, log_sync, log_async, log_avg_cv_sp, productivity, productivity_f)
  )
scaled_sim_sem <- sim_sem %>%
  mutate(across(where(is.double), ~scale(.x)[,1]))
```

```{r}
pred_may <- "log1_avg_max_int_alive*log_richness*ct_alive*productivity + env_stoch"
rand <- "(1 | Z)"

mod_may_single <- lm(formula(str_replace_all(paste0("log_stab_com ~ ", pred_may), "\\*", "+")),
  scaled_sim_sem)
performance::check_collinearity(mod_may_single)
```

```{r}
mod_may <- glmmTMB(formula(paste0("log_stab_com ~ ", pred_may, " + ", rand)), scaled_sim_sem)

r2_nakagawa(mod_may)
par_mod_may <- parameters(mod_may)
plot(parameters(mod_may))
```

```{r}
mod_may_sync <- glmmTMB(formula(paste0("log_sync ~ ", pred_may, " + ", rand)),
  scaled_sim_sem)
r2_nakagawa(mod_may_sync)
plot(parameters(mod_may_sync))
```

```{r}
mod_may_cv_sp <- glmmTMB(formula(paste0("log_avg_cv_sp ~ ", pred_may, " + ", rand)),
  scaled_sim_sem)
r2_nakagawa(mod_may_cv_sp)
plot(parameters(mod_may_cv_sp))
```

## Rho model

- Should be include also the monotrophic communities ? I.e. Communities
  containing only plants?

```{r}
sim_rho %>%
  filter(ct_alive == 0, env_stoch == 0.5) %>%
  ggplot(aes(x = log_richness, y = log_stab_com)) +
  geom_point() +
  geom_smooth() +
  facet_grid(cols = vars(rho), rows = vars(productivity_f))
```

```{r}
pred_rho <- "log_richness +
ct_alive +
log1_avg_max_int_alive +
productivity +
rho +
I(rho^2) +
env_stoch +

log_richness:ct_alive +
log_richness:log1_avg_max_int_alive +
log_richness:productivity +
log_richness:rho +

log1_avg_max_int_alive:ct_alive +
log1_avg_max_int_alive:productivity +
log1_avg_max_int_alive:rho +

ct_alive:rho +
ct_alive:productivity +
rho:productivity +
I(rho^2):productivity +

log_richness:log1_avg_max_int_alive:ct_alive +
log_richness:log1_avg_max_int_alive:productivity +
log_richness:log1_avg_max_int_alive:rho +
log_richness:ct_alive:productivity +
log_richness:ct_alive:rho +
log_richness:rho:productivity +

log1_avg_max_int_alive:ct_alive:rho +
log1_avg_max_int_alive:ct_alive:productivity +
log1_avg_max_int_alive:rho:productivity +

ct_alive:rho:productivity"
rand <- "(1 | Z)"

mod_rho_single <- lm(formula(str_replace_all(paste0("log_stab_com ~ ", pred_rho), "(\\*|:)", "+")),
  sim_rho_scaled)
performance::check_collinearity(mod_rho_single)
```

```{r}
model2tibble <- function(x, response = NULL) {
  out <- parameters(x) %>%
    filter(Effects == "fixed", Parameter != "(Intercept)") %>%
    as_tibble() %>%
    janitor::clean_names() %>%
    mutate(
      response = var_replacement()[as.character(formula(x)[2])],
      parameter = str_replace_all(parameter, var_replacement()),
      count_int = str_count(parameter, ":"),
      effect_type = case_when(
        count_int == 0 ~ "single",
        count_int == 1 ~ "double",
        count_int == 2 ~ "triple",
        TRUE ~ "other"

      )
    ) %>%
    select(response, parameter:ci_high, effect_type)
    out
}
plot_effect_type <- function(x) {
  effect <- c("single", "double", "triple")
  p <- map(effect,
    function(y) {
      x %>%
        filter(effect_type == y) %>%
        arrange(coefficient) %>%
        ggplot(aes(
            y = reorder(parameter, -coefficient),
            x = coefficient,xmin = ci_low, xmax = ci_high,
            color = response
            )) +
        geom_vline(xintercept = 0, color = "black", linetype = "dashed", linewidth = 1.5) +
        geom_pointrange(position = position_dodge(width = 0.5)) +
        labs(x = "Standardized Coefficients")
    }
  )
  names(p) <- effect
  p
}
```

```{r}
mod_rho_scaled <- map(setNames(
    c("log_stab_com", "log_stab_pop", "log_async"),
    c("log_stab_com", "log_stab_pop", "log_async")
    ),
  function (x) {
    glmmTMB(formula(paste0(x, " ~ ", pred_rho, " + ", rand)),
      sim_rho_scaled)
  }
)
coef_mod_rho_scaled <- map_dfr(mod_rho_scaled, ~model2tibble(.x))
ti <- map_dfr(mod_rho_scaled, ~as.data.frame(r2_nakagawa(.x)), .id = "response") %>%
  mutate(response = var_replacement()[response])
p_mod_rho_scaled <- plot_effect_type(coef_mod_rho_scaled)
plot_grid(plotlist = p_mod_rho_scaled)
```

```{r}
mod_rho <- map(setNames(
    c("log_stab_com", "log_stab_pop", "log_async"),
    c("log_stab_com", "log_stab_pop", "log_async")
    ),
  function (x) {
    glmmTMB(formula(paste0(x, " ~ ", pred_rho, " + ", rand)),
      sim_rho)
  }
)
coef_mod_rho <- map_dfr(mod_rho, ~model2tibble(.x))
ti <- map_dfr(mod_rho, ~as.data.frame(r2_nakagawa(.x)), .id = "response") %>%
  mutate(response = var_replacement()[response])
p_mod_rho <- plot_effect_type(coef_mod_rho)
plot_grid(plotlist = p_mod_rho)
```

@@

```{r}
pred_list <- list(
  log_richness = c(log(1), log(5), log(10), log(20), log(30), log(50)),
  ct_alive = c(0, .10, .20),
  rho = c(0, .5, 1),
  log1_avg_max_int_alive = c(log(0 + 1), round(log(.81 + 1), 1), round(log(5.65 + 1), 1)),
  env_stoch = .5,
  productivity = c("basic", "enrichment"),
  Z = 100
)
pred_rho <- expand.grid(pred_list) %>%
  filter(
    !(log1_avg_max_int_alive == 0 & ct_alive != 0 | ct_alive == 0 & log1_avg_max_int_alive != 0)
  )

pred_rho$log_stab_com <- predict(mod_rho[["log_stab_com"]], newdata = pred_rho)

pred_rho %>%
  ggplot(aes(
      y = log_stab_com,
      x = log_richness,
      color = factor(ct_alive),
      linewidth = factor(log1_avg_max_int_alive)
      )) +
  geom_line() +
  facet_grid(
    rows = vars(rho),
    cols = vars(productivity)
  )
```

@@

```{r}
sim_rho_pers <- simZ %>%
  mutate(across(c(S, ct, avg_max_int, gini_max_int), log, , .names = "log_{.col}")) %>%
  mutate(
    log1_avg_max_int = log(avg_max_int + 1),
    productivity_f = factor(productivity)
    ) %>%
  as.data.frame() %>%
  select(c(
      log_S, ct, max_tlvl, Z, rho,
      gini_max_int, avg_max_int, log1_avg_max_int, env_stoch,
      productivity, productivity_f,
      persistence)
  )
sim_rho_pers_scaled <- sim_rho_pers %>%
  mutate(across(where(is.double), ~scale(.x)[,1]))

@@

```{r}
```

@@

```{r}
library(ipred)
ctrl <- trainControl(method = "cv",  number = 10)

@@

```{r}
ctrl <- trainControl(method = "cv",  number = 10)

# CV bagged model
bagged_cv <- train(
  stab_com ~ richness + ct_alive + rho + productivity + max_tlvl_alive +
    avg_max_int_alive,
  data = simZ,
  cp = .2,
  maxdepth = 6,
  method = "treebag",
  trControl = ctrl,
  importance = TRUE
  )
plot(varImp(bagged_cv), 20)
plot(bagged_cv)
```

```{r}
m1 <- rpart(
  formula = stab_com ~ richness + ct_alive + rho + productivity + max_tlvl_alive +
    avg_max_int_alive,
  data    = simZ,
  method  = "anova"
  )
rpart.plot(m1)
```

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.pos = "H",  # pdf mode
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE,
  fig.path="figures/"
)
```

@@

library(rpart)
library(rpart.plot)
library(caret)
library(ipred)
library(kableExtra)

@@

- Response diversity is key in driving stability in ecological communities
- Response diversity control asynchrony with richness
- Mainly done in plants or in same food-web modules
- Food-webs structure can also modulate synchrony and population stability by
  the strength of trophic interactions

@@

For me, there are two ways to see the question.

@@

## What is the effects of species richness on stability facing multiple stressors in competitive and food-webs communities?

@@

- Important bits:
  - Niche model (Connectance highly constrained by richness)
  - Type III functional response
  - No predator interference
  - Enrichment: K = 1 or 20
  - Standardized carrying capacity (Remove the effect of species richness on
    total biomass, i.e. remove the effect of niche complementarity on biomass
    produced by primary producers)

@@

- S: 5 to 60
- C: .02 to .3
- K: 1 and 20
- $\rho$: 0 to 1
- Z: 5 to 1000

@@

```{r}
cor_enrich <- cor(simZ %>%
    filter(productivity == "enrichment") %>%
    select(c(S, richness, ct, Z, ct_alive, total_biomass, avg_max_int_alive,
        sd_max_int_alive, cv_max_int_alive,
        gini_max_int_alive,
        w_avg_tlvl_alive, max_tlvl_alive, rho, env_stoch, stab_com, avg_cv_sp,
        sync)) %>% na.omit(),
    method = "spearman")
cor_basic <- cor(simZ %>%
    filter(productivity == "basic") %>%
select(c(S, richness, ct, Z, ct_alive, total_biomass, avg_max_int_alive,
        sd_max_int_alive, cv_max_int_alive,
        gini_max_int_alive,
        w_avg_tlvl_alive, max_tlvl_alive, rho, env_stoch, stab_com, avg_cv_sp,
        sync)) %>% na.omit(),
    method = "spearman")
p_cor_basic <- ggcorrplot(cor_basic, type = "lower",
   lab = TRUE)
p_cor_enrich <- ggcorrplot(cor_enrich, type = "lower",
   lab = TRUE)
p_cor <- plot_grid(
  p_cor_basic,
  p_cor_enrich,
  ncol = 2,
  labels = "auto"
)
ggsave(here("report", "figures", "p_cor.pdf"),
  plot = p_cor,
  device = NULL,
  path = NULL,
  scale = 3.0,
  units = "mm",
  width = 140,
  height = 140 * .5,
  dpi = 300,
  limitsize = TRUE,
  bg = NULL
)
```

```{r}
cor_cap <- "Correlation among foodweb structure and stability for basic (a) and
enriched (b) environments."
```

```{r, fig.cap=cor_cap}
knitr::include_graphics(here::here("report", "figures", "p_cor.pdf"))
```

```{r}
sim_rich_prod <- simZ %>%
  filter(
    env_stoch == .5
  )
```

```{r}
p_sim_rich_prod <- sim_rich_prod %>%
  mutate(stab_pop = 1/ avg_cv_sp) %>%
  pivot_longer(
    c(stab_com, stab_pop, sync),
    names_to = "metric",
    values_to = "stab") %>%
  mutate(
    metric = var_replacement()[metric],
    rho = rho_replacement()[as.character(rho)]
  ) %>%
  ggplot(aes(x = richness, y = stab, color = factor(productivity))) +
  geom_point(alpha = .1, shape = 20) +
  geom_smooth() +
  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
  labs(
    color = "Productivity",
    x = "Species richness",
    y = "Stability component"
  ) +
  scale_x_continuous(
    sec.axis = sec_axis(~ . ,
      name = "Response diversity",
      breaks = NULL,
      labels = NULL)
  )
ggsave(
  filename = here::here("report", "figures", "stability_rich.pdf"),
  p_sim_rich_prod,
  scale = 1.8,
  width = 88,
  height = 88 * .6,
  units = "mm"
)
```

```{r}
p_sim_rich_prod_fw_only <- sim_rich_prod %>%
  filter(ct_alive != 0, avg_max_int_alive != 0) %>%
  mutate(stab_pop = 1/ avg_cv_sp) %>%
  pivot_longer(
    c(stab_com, stab_pop, sync),
    names_to = "metric",
    values_to = "stab") %>%
  mutate(
    metric = var_replacement()[metric],
    rho = rho_replacement()[as.character(rho)]
  ) %>%
  ggplot(aes(x = log(richness), y = log(stab), color = factor(productivity))) +
  geom_point(alpha = .1, shape = 20) +
  geom_smooth(method = "lm") +
  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
  labs(
    color = "Productivity",
    x = "Species richness",
    y = "Stability component"
  ) +
  scale_x_continuous(
    sec.axis = sec_axis(~ . ,
      name = "Response diversity",
      breaks = NULL,
      labels = NULL)
  )
ggsave(
  filename = here("report", "figures", "p_sim_rich_prod_fw_only.pdf"),
  p_sim_rich_prod_fw_only,
  scale = 1.8,
  width = 88,
  height = 88 * .6,
  units = "mm"
)
```

```{r}
p_sim_rich_prod_p_only <- sim_rich_prod %>%
  filter(ct_alive == 0) %>%
  mutate(stab_pop = 1/ avg_cv_sp) %>%
  pivot_longer(
    c(stab_com, stab_pop, sync),
    names_to = "metric",
    values_to = "stab") %>%
  mutate(
    metric = var_replacement()[metric],
    rho = rho_replacement()[as.character(rho)]
  ) %>%
  ggplot(aes(x = richness, y = stab, color = factor(productivity))) +
  geom_point(alpha = .1, shape = 20) +
  geom_smooth() +
  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
  labs(
    color = "Productivity",
    x = "Species richness",
    y = "Stability component"
  ) +
  scale_x_continuous(
    sec.axis = sec_axis(~ .,
      name = "Response diversity",
      breaks = NULL,
      labels = NULL)
  )
ggsave(
  filename = here("report", "figures", "p_sim_rich_prod_p_only.pdf"),
  p_sim_rich_prod_p_only,
  scale = 1.8,
  width = 88,
  height = 88 * .6,
  units = "mm"
)
```

```{r, fig.cap = "Food-Web only."}
knitr::include_graphics(here("report", "figures", "p_sim_rich_prod_fw_only.pdf"))
```

```{r, fig.cap = "Primary producers only."}
knitr::include_graphics(here::here("report", "figures", "p_sim_rich_prod_p_only.pdf"))
```

- Enrichment decreases the effect of response diversity of stability
- Enrichment increases synchrony
- Richness decreases population stability, but increases it in absence of response
  diversity
- Food-web maintains some asynchrony despite the absence of response
  diversity but synchrony increase with richness in basic environment

@@

# Food-web structure and interaction strength drive stability

@@

```{r}
sim_sem <- simZ %>%
  filter(ct_alive != 0, env_stoch == 0.5, rho == 0) %>%
  mutate(across(c(async, stab_pop, stab_com, richness, ct_alive, sd_max_int_alive, avg_max_int_alive), log, , .names = "log_{.col}")) %>%
  mutate(
    log1_avg_max_int_alive = log(avg_max_int_alive + 1),
    log1_sd_max_int_alive = log(sd_max_int_alive + 1),
    productivity_f = factor(productivity)
    ) %>%
  as.data.frame()
scaled_sim_sem <- sim_sem %>%
  mutate(across(where(is.double), ~scale(.x)[,1]))
```

```{r}
var_fw_struct <- c("richness", "ct_alive", "Z")
var_fw_emergent_struct <- c("max_tlvl_alive", "w_avg_tlvl_alive")
var_fw_flux <- c("gini_max_int_alive", "avg_max_int_alive", "sd_max_int_alive",
  "cv_max_int_alive")
var_stab <- c("async", "stab_com", "stab_pop")
```

```{r}
#colnames(simZ)
pairs(sim_sem %>%
  filter(env_stoch == .5) %>%
  select(c(var_fw_struct, var_fw_emergent_struct, var_fw_flux, stab_pop)))
```

```{r, eval = FALSE}
performance::check_collinearity(lm(w_avg_tlvl_alive ~ max_tlvl_alive,sim_sem))
performance::check_collinearity(lm(w_avg_tlvl_alive ~ ct_alive + richness,sim_sem))
performance::check_collinearity(lm(w_avg_tlvl_alive ~ ct_alive + richness,sim_sem))
performance::check_collinearity(lm(avg_max_int_alive ~ w_avg_tlvl_alive + ct_alive + richness,sim_sem))
performance::check_collinearity(lm(avg_max_int_alive ~ max_tlvl_alive + ct_alive,sim_sem))
performance::check_collinearity(lm(stab_com ~ log_richness + log1_avg_max_int_alive + log1_sd_max_int_alive + w_avg_tlvl_alive + ct_alive,sim_sem))
performance::check_collinearity(lm(stab_com ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive,sim_sem))
```

```{r}
sem_list_basic <- list(
  w_avg_tlvl_alive = lm(w_avg_tlvl_alive ~ richness + ct_alive, sim_sem),
  sd_max_int_alive = lm(sd_max_int_alive ~ richness + ct_alive + w_avg_tlvl_alive, sim_sem),
  avg_max_int_alive = lm(avg_max_int_alive ~ richness + ct_alive + w_avg_tlvl_alive, sim_sem),
  log_async = lm(log_async ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive, sim_sem),
  log_stab_pop = lm(log_stab_pop ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive, sim_sem),
  log_stab_com = lm(log_stab_com ~ log_async + log_stab_pop, sim_sem)
)
sem_basic <- as.psem(sem_list_basic)
```

```{r}
ti <- summary(sem_basic)$coefficients[, c(1, 2, 8, 9)]
colnames(ti)[4] <- "Signif"
ti %>%
  mutate(
    Response = var_replacement()[Response],
    Predictor = var_replacement()[Predictor]
  ) %>%
  kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
  collapse_rows(1, valign = "middle") %>%
  kable_styling()
```

```{r, eval = FALSE}
ti <- map_dfr(setNames(sem_list_basic, names(sem_list_basic)),
  performance::check_collinearity,
  .id = "response") %>%
  as_tibble
ti %>%
  mutate(
    response = var_replacement()[response],
    Term = var_replacement()[Term]
  ) %>%
  kable(caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
  kable_styling()
```

```{r, eval = FALSE}
map_dfr(sem_list_basic, rsquared) %>%
  mutate(Response = var_replacement()[Response]) %>%
  select(Response, R.squared) %>%
  kable(caption = "Rsquared for the Structural Equation Model.") %>%
  kable_styling()
```

```{r}
sim_sem_nodivresp <- simZ %>%
  filter(ct_alive != 0, env_stoch == 0.5, rho == 1) %>%
  mutate(across(c(async, stab_pop, stab_com, richness, ct_alive, sd_max_int_alive, avg_max_int_alive), log, , .names = "log_{.col}")) %>%
  mutate(
    log1_avg_max_int_alive = log(avg_max_int_alive + 1),
    log1_sd_max_int_alive = log(sd_max_int_alive + 1),
    productivity_f = factor(productivity)
    ) %>%
  as.data.frame()
```

```{r}
sem_list_nodivresp <- list(
  w_avg_tlvl_alive = lm(w_avg_tlvl_alive ~ richness + ct_alive, sim_sem_nodivresp),
  sd_max_int_alive = lm(sd_max_int_alive ~ richness + ct_alive + w_avg_tlvl_alive, sim_sem_nodivresp),
  avg_max_int_alive = lm(avg_max_int_alive ~ richness + ct_alive + w_avg_tlvl_alive, sim_sem_nodivresp),
  log_async = lm(log_async ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive, sim_sem_nodivresp),
  log_stab_pop = lm(log_stab_pop ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive, sim_sem_nodivresp),
  log_stab_com = lm(log_stab_com ~ log_async + log_stab_pop, sim_sem_nodivresp)
)
sem_nodivresp <- as.psem(sem_list_nodivresp)
```

```{r}
coef_sem_nodivresp <- summary(sem_nodivresp)$coefficients[, c(1, 2, 8, 9)]
colnames(coef_sem_nodivresp)[4] <- "Signif"
coef_sem_nodivresp %>%
  mutate(
    Response = var_replacement()[Response],
    Predictor = var_replacement()[Predictor]
  ) %>%
  kable(caption = "Standardized estimates for the Structural Equation Models with no response diversity.") %>%
  collapse_rows(1, valign = "middle") %>%
  kable_styling()
```

# Effect of multiple stressors on stability in monotrophic and food-webs

```{r}
tar_load(p_mod_rho_scaled)
p_mod_rho_scaled_tot <- plot_grid(plotlist = p_mod_rho_scaled)
ggsave(here("report", "figures", "p_mod_rho_scaled_tot.pdf"),
  plot = p_mod_rho_scaled_tot,
  device = NULL,
  path = NULL,
  scale = 2.4,
  units = "mm",
  width = 140,
  height = 140 * .5,
  dpi = 300,
  limitsize = TRUE,
  bg = NULL
)
```

```{r, eval = FALSE}
tar_load(p_mod_rho)
plot_grid(plotlist = p_mod_rho)
```

@@

```{r}
tar_load(pred_rho)
p_pred_rho <- pred_rho %>%
  mutate(rho = rho_replacement()[as.character(rho)]) %>%
  ggplot(aes(
      y = log_stab_com,
      x = log_richness,
      color = factor(ct_alive),
      linewidth = factor(log1_avg_max_int_alive)
      )) +
  geom_line() +
  labs(
    color = "Connectance",
    linewidth = "Avg interaction strength",
    y = "Community stability",
    x = "Species richness (log)"
    ) +
  facet_grid(
    rows = vars(rho),
    cols = vars(productivity)
  )
ggsave(here("report", "figures", "p_pred_rho.pdf"),
  plot = p_pred_rho,
  device = NULL,
  path = NULL,
  scale = 2.4,
  units = "mm",
  width = 140,
  height = 140 * .5,
  dpi = 300,
  limitsize = TRUE,
  bg = NULL
)
```

```{r}
predS_cap <- "Predictions for the model of drivers of community stability in
basic and enriched environments (columns) and across varying response diversity
(rows)."
```

```{r predS, fig.cap = predS_cap}
knitr::include_graphics(here("report", "figures", "p_pred_rho.pdf"))
```

```{r}
coef_rho_cap <- "Coefficients for the model of drivers of community stability,
population stability and asynchrony. See predictions for a more simple overview."
```

```{r coef-rho, fig.cap = coef_rho_cap}
knitr::include_graphics(here("report", "figures", "p_mod_rho_scaled_tot.pdf"))
```

- From the predictions of the model:
  - Stong interaction among interaction strength, connectance and species
    richness, enrichment and response diversity = *Food-web structure effects on
    stability is context dependant*
  - High connectance and high interaction strength is generally destabilizing,
    driving negative relationships between stability and species richness in
    enrichment context (high $K$)
  - At the reverse, low connectance and high interaction strength is stabilizing
  - In basic environment, high interaction strength stabilise the community
    biomass in the absence of response diversity. At the opposite, low
    interaction strength generate a negative stability richness relationship.
  - In enrichment context, response diversity has little effect on stability!
  - In enrichment context, High interaction strength is generally stabilizing!

@@

```{r, eval = FALSE}
sim_rho_pers <- simZ %>%
  mutate(across(c(S, ct, avg_max_int, gini_max_int), log, , .names = "log_{.col}")) %>%
  mutate(
    log1_avg_max_int = log(avg_max_int + 1),
    productivity_f = factor(productivity)
    ) %>%
  as.data.frame() %>%
  select(c(
      log_S, ct, max_tlvl, Z, rho,
      gini_max_int, avg_max_int, log1_avg_max_int, env_stoch,
      productivity, productivity_f,
      persistence)
  )
sim_rho_pers_scaled <- sim_rho_pers %>%
  mutate(across(where(is.double), ~scale(.x)[,1]))

@@

@@

```{r, eval = FALSE}
library(ipred)
ctrl <- trainControl(method = "cv",  number = 10)

@@

```{r, fig.cap = "Variable importance from bagged regression tree."}
ctrl <- trainControl(method = "cv",  number = 10)

# CV bagged model
bagged_cv <- train(
  stab_com ~ richness + ct_alive + max_tlvl_alive +
    w_avg_tlvl_alive + avg_max_int_alive + sd_max_int_alive + rho + productivity,
  data = simZ %>% filter(ct_alive != 0, avg_max_int_alive != 0),
  cp = .2,
  maxdepth = 6,
  method = "treebag",
  trControl = ctrl,
  importance = TRUE
  )
plot(varImp(bagged_cv), 8)
```

```{r, fig.cap="Regression tree "}
m1 <- rpart(
  formula = stab_com ~ richness + ct_alive + rho + productivity + w_avg_tlvl_alive + max_tlvl_alive +
    avg_max_int_alive + sd_max_int_alive,
  data    = simZ %>%
    filter(ct_alive != 0, avg_max_int_alive != 0),
  method  = "anova"
  )
rpart.plot(m1)
```
